Paper 1 Analysis

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
New CSP models and code.

<<Models_CSP>>=
fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
if (FALSE && !rerunModels){
  # load from the file on disk
  modelsCSP <- readRDS(fileNameCSP)
} else {
  #
  # Models that adhere to the cost-share theorem
  #

  modelsCSP <- list()
  # Output elasticities based on cost share principle
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      print(adj)
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      formula <- substitute(
        log(Y) - alpha_1 * log(K) - alpha_2 * log(L) ~ T,
        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
      )
      # Cobb-Douglas
      cdModCSP <- 
        eval(substitute( 
          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
              optimize = FALSE),
          list(formula = formula)))

@@

temp_data_exp <- 
  leaf_apply(
    modelsExp, class=c("lm"), 
    f = function(model, id){
      model$dat %>% 
        select(Year, Country) %>%
        mutate(
          Country = as.character(Country),  # to avoid warning about unmatched levels of factors
          fittedExp = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
          residualsExp = resid(model)     
        )
    }
  ) %>% 
  bind_rows()

@@

function_that_was_here_before <- function(model, id){
  id_list <- strsplit(id, split = "[.]")[[1]]
  out <- model$data %>% 
    select(Year) %>%
    mutate(
      # By including [c(1:length(df$Year))] on the end, we 
      # add NAs (as appropriate) to the end of these columns
      # if data do not exist.
      fitted = yhat(model)[c(1:length(Year))],
      Residuals = resid(model)[c(1:length(Year))],
      Country = id_list[[1]],
      flavor = if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted",
      energy = if (id_list[[3]] == "noE") "Without energy" else "With energy",
      model = id_list[[4]],
      nest = if (length(id_list) > 4) id_list[[5]] else NA
    )
  # Now add the response, using the original variable name.
  out[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(out$Year))]
  return(out)  
}

>>>>

<<Models_CSP>>=
fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
if (!rerunModels){
  # load from the file on disk
  modelsCSP <- readRDS(fileNameCSP)
} else {
  #
  # Models that adhere to the cost-share theorem
  #

  modelsCSP <- list()
  # Output elasticities based on cost share principle
  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
  betaCSP <- 0.7 # Fraction of national accounts spent on labor
  for (country in countries){
    for (adj in c("unadjusted", "adjusted")){
      # Replace with better code later. 
      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
      # or something like that.
      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
      yVar <- as.name(summands(form, n=1, right=FALSE))
      kVar <- as.name(summands(form, n=1))
      lVar <- as.name(summands(form, n=2))
      tVar <- as.name(summands(form, n=3))
      data <- historicalData[[country]]
      formula <- substitute(
        log(Y) - alpha_1 * log(K) - alpha_2 * log(L) ~ T,
        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
      )
      # Cobb-Douglas
      cdModCSP <- 
        eval(substitute( 
          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
              optimize = FALSE),
          list(formula = formula)))

@@

temp_data_exp <- 
  leaf_apply(
    modelsExp, class=c("lm"), 
    f = function(model, id){
      model$dat %>% 
        select(Year, Country) %>%
        mutate(
          Country = as.character(Country),  # to avoid warning about unmatched levels of factors
          fitted = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
          residuals = resid(model)     
        )
    }
  ) %>% 
  bind_rows()

@@

function_that_was_here_before <- function(model, id){
  id_list <- strsplit(id, split = "[.]")[[1]]
  out <- model$data %>% 
    select(Year) %>%
    mutate(
      # By including [c(1:length(df$Year))] on the end, we 
      # add NAs (as appropriate) to the end of these columns
      # if data do not exist.
      fitted = yhat(model)[c(1:length(Year))],
      residuals = resid(model)[c(1:length(Year))],
      Country = id_list[[1]],
      flavor = ifelse (id_list[[2]] ==  "unadjusted", "Unadjusted", "Quality-adjusted"),
      energy = ifelse(id_list[[3]] == "noE", "Without energy", "With energy"),
      model = id_list[[4]],
      nest = ifelse (length(id_list) > 4, id_list[[5]], NA)
    )
  # Now add the response, using the original variable name.
  out[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(out$Year))]
  return(out)  
}

### 2015-10-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New CSP models and code.

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital, labor, and energy.">>=
ggplot(
  data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l, cs_e)
  ) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l", "e"),
                     values=c("black", "black", "gray70")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l", "e"),
                        values=c(2,3,1)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l", "e"),
                    values = c(0.9, 0.9, 0.6)) +
  xy_theme()
@

>>>>

<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.">>=
ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
  geom_line(mapping = aes(
    x = Year, 
    y = value, 
    group = cost_share, 
    linetype = cost_share,
    color = cost_share,
    size = cost_share)) +
  facet_grid( ~ Country) +
  ylab("Cost Share") +
  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
  xlab("") +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_color_manual(name = "", 
                     labels=c("k", "l"),
                     values=c("black", "black")) +
  scale_linetype_manual(name="", 
                        labels=c("k", "l"),
                        values=c(2,3)) + 
  scale_size_manual(name="", 
                    labels=c("k", "l"),
                    values = c(0.9, 0.9)) +
  xy_theme()
@
